---
title: "Lab 5: Poisson Lab"
subtitle: "Lab 5"
editor: visual
execute: 
  message: false
  warning: false
---

## Introduction

This lab aims to provide students with hands-on experience in running Poisson or negative binomial models, as well as reporting, interpreting, and visualizing results.

## Instructions:

- If you are fitting a model, display the model output in a neatly formatted table. (The \`tidy\` and \`kable\` functions can help!).

- If you are creating a plot, use clear labels for all axes, titles, etc.

- Commit and push your work to GitHub regularly, at least after each exercise. Write short and informative commit messages.

- When you're done, we should be able to knit the final version of the QMD in your GitHub as a HTML.

1.  To complete this lab:

-   Load packages

```{r}
library(MASS) # must be loaded before tidy or chaos will ensue
library(tidyverse)
library(mice)
library(emmeans)
library(ggeffects)
library(easystats)
library(performance)

```

-   Download the dataset:

```{r}
data <- read_delim("https://raw.githubusercontent.com/jgeller112/psy504-advanced-stats/main/slides/Poisson/data/2010.csv")


```

3.  Read the preregistration document (preregis.qmd)

    -   Look at the `2010 Dataset Coder.pdf` for information about vars and missing labels.

4.  Determine what test to run: Poisson or a negative binomial model

5.  Create a new document - Report the results in APA style and include the following:

    -   Missing data information

    -   Model fit

    -   LRT $\chi^2$ values for each effect (if categorical, include relevant comparisons, if applicable)

    -   A figure focusing on one of the predictors (i.e., the one that is most interesting to you)

        -   You may select any predictor from the model that interests you

6.  Upload your analysis script and html (Results + Figures) to Github
